The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/ms.tex
Fig. 7
Fig. 6

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/compare_ebin_idist.pdf}
        \caption{
            Same as Figure \ref{fig:ebin}, but with the mutual inclination distribution given by equation (\ref{eq:idist}).
        }
        \script{compare_ebin_idist.py}
        \label{fig:ebin-idist}
    \end{centering}
\end{figure*}

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/fpol_j_idist.pdf}
        \caption{
            Same as Figure \ref{fig:fpol_j}, but with the mutual inclination distribution given by equation (\ref{eq:idist}).
        }
        \script{f_p_of_j_idist.py}
        \label{fig:fpol_j-idist}
    \end{centering}
\end{figure*}

>>>>

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/compare_ebin_idist.pdf}
        \caption{
            Same as Figure \ref{fig:ebin}, but with the mutual inclination distribution given by equation (\ref{eq:idist}). \RR{When $j$ is low, lower inclination preferences decrease $f_\text{polar}$ around $e_\text{b}\sim0.5$, but have little effect near 0 and 1. In the high-$j$ regime, low inclinations lower the value that $f_\text{polar}$ tends to as $e_\text{b}\rightarrow 0$. {\bf Insert}: Mutual inclination probability distribution normalized by $\sin i$. This normalization shows that the probability-per-unit-area on the unit sphere becomes very high at $i=0$ (coplanar alignment) when $\sigma$ is small (dashed and dotted lines), but it is uniform everywhere in the isotropic case ($\sigma \rightarrow \infty$, solid line).}
        }
        \script{compare_ebin_idist.py}
        \label{fig:ebin-idist}
    \end{centering}
\end{figure*}

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/fpol_j_idist.pdf}
        \caption{
            Same as Figure \ref{fig:fpol_j}, but with the mutual inclination distribution given by equation (\ref{eq:idist}). \RR{Preference for lower mutual inclinations (lower values of $\sigma$, see dashed and dotted lines) lead to lower $f_\text{polar}$ in all cases. See the inset of Figure \ref{fig:ebin-idist} for a visualization of the various $i$ distributions.}
        }
        \script{f_p_of_j_idist.py}
        \label{fig:fpol_j-idist}
    \end{centering}
\end{figure*}
